### 2015-10-28 manuscript.Rnw
appendix

<<cat_map, purl=TRUE, echo=FALSE, size='small', fig.height=4.2, results='hide', message=FALSE, cache=TRUE, fig.cap='GBIF records for the species in \\textit{Lynx} included in the phylogeny associated with the study by \\citealt{Johnson2006}'>>=
## load required packages
library(rgbif)
library(ggplot2)
library(maps)

>>>>

<<cat_map, purl=TRUE, echo=FALSE, size='small', fig.height=4.2, results='hide', message=FALSE, cache=TRUE, fig.cap='GBIF records for the species in \\textit{Lynx} included in the phylogeny associated with the study by \\citealt{Johnson2006}'>>=
## load required packages
library(rotl)
library(rgbif)
library(ggplot2)
library(maps)

## Import the felid tree using study and tree IDs discovered with 
## studies_find_studies() in the manuscript
cat_tree <- get_study_tree(study_id ="pg_1981",                           
                           tree_id = "tree4052")
